The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
Rewrote paragraph about altinternet repository partially

	We made a significant contribution to this project index. We have improved and updated the list of these decentralized systems. For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), age, number of contributors and commits, activity and (main) programming language, sourced from Ohloh. This table is available on the same Github repository.

	An excerpt of the table is included as table \ref{tbl:altinternet}. In this instance, we chose to sort the table on the number of commits, because we found that this most accurately represents both the maturity and activity of the projects. Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects.

@@

	% Tabel moet nog mooi gemaakt worden
	\begin{table}
		\centering
		\include{tbl-alternativeinternet}
		\caption{The top 10 projects from the Alternative Internet repository by number of commits (as of 2014-03-15).}
		\label{tbl:altinternet}
	\end{table}

>>>>

	We made a significant contribution to this project index. We created a table containing each of the listed systems that shows statistics such as the total lines of code (LOC), age, number of contributors and commits, activity and (main) programming language, sourced from Ohloh. This should make it easier to filter out poorly maintained or otherwise deprecated projects. The table is available on the same Github repository.

	An excerpt of the table is included as table \ref{tbl:altinternet}. In this instance, we chose to sort the table on the number of commits, because we found that this most accurately represents both the maturity and activity of the projects. Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects in their repository.

@@

	\begin{table}
		\centering
		\include{tbl-alternativeinternet}
		\caption{The top 10 projects from the Alternative Internet repository by number of commits (as of 2014-03-15).}
		\label{tbl:altinternet}
	\end{table}
